The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine Cells as Calibrators\altaffilmark{1}

### 2016-03-01 telluric/ms.tex
More text in telluric introduction.

The current best RV precision is around 1~m/s, attainable via two
wavelength calibration methods: ThAr lamp emission line calibration
(e.g., ELODIE and HARPS; \citealt{elodie, harps-s}) and iodine cell
absorption line calibration (e.g., Keck/HIRES; \citealt{butler1996}).

One of the contributing term comes from Earth's atmospheric
absorption, which imprints telluric lines onto the observed stellar
spectrum. Deep tellurics are thrown out, while micro-tellurics
(define; \citealt{hitran2013}) remain and they are very hard to deal
with. The contamination from the micro-telluric lines has an adverse
effect on the RV precision, and such effect is characterized for the
HARPS-N spectrograph, which is ThAr calibrated, by \cite{artigau2014}
and \cite{cunha2014}.

>>>>

The current best RV precision is around 1~m/s \citep{eprv2015},
attainable via two wavelength calibration methods in the optical band:
ThAr lamp emission line calibration (e.g., ELODIE and HARPS;
\citealt{elodie, harps-s}; $\sim$400-690~nm) and iodine cell
absorption line calibration (e.g., Keck/HIRES and Magellan/PFS;
\citealt{butler1996, 2010SPIE.7735E..53C}; $\sim$500-620~nm). The
major obstacles for achieving a higher RV precision are: stellar
activity induced RV signals, instrumental effects, telluric
contamination, and limitation in data analysis \citep{eprv2015}.

Traditionally, telluric contamination is not considered as problematic
for precise RV in the optical. It is certainly a sever source of
spectral contamination and a bottleneck for achieving higher RV
precision in the near infra-red region (e.g.,
\citealt{2010ApJ...713..410B}), where a large number of deep water and
methane lines reside. However, there is only a small wavelength
range in the optical that has deep telluric lines, and typically such
regions are simply thrown out for the purpose of precise RV analysis,
either by giving them zero weights in the cross correlation masks (for
ThAr calibrated spectra, e.g., \citealt{2002A&A...388..632P}) or
flagging them as bad pixels (for iodine calibrated spectra, e.g., for
Keck/HIRES).

Recently, the works by \cite{artigau2014} and \cite{cunha2014} have
characterized and mitigated the effects of telluric contamination in
the precise RV data taken by the ThAr-calibrated HARPS-S.
\cite{cunha2014} focuses on the issues with ``micro-telluric" lines
(shallow telluric absorption lines with $<1$-3\% depths), which are
recognized for the first time. \cite{cunha2014} fit and then divide
out the telluric lines in the observed spectra using synthetic
telluric spectra generated by the LBLRTM package (Line-By-Line
Radiative Transfer Model, \citealt{lblrtm}; with line lists from
HIgh-resolution TRANsmission molecular absorption database, or HITRAN,
\citealt{hitran2013}) and also TAPAS \citep{tapas}, which is a more
user-friendly but less flexible package wrapper using LBLRTM. They
concluded that the micro-tellurics have an impact (defined as RMS of
difference between RVs before and after micro-telluric removal) of
$\sim$10-20 cm/s for G stars observed with low to moderate air masses,
but the impact can be substantial in some cases to up to $\sim$0.5-1
m/s. \cite{artigau2014} uses principal component analysis (PCA) to
empirically correct for telluric lines in HARPS-S data (both
micro-tellurics and the deep lines in the $\sim$630~nm region), and
combined PCA with rejection masking, they reduced the RV RMS by
$\sim$20~cm/s (and more significantly for the $\sim$630~nm region).

% I'm here:
This paper focuses on the adverse effects of telluric contamination
and its remedies under the context of iodine-calibrated precise RV,
especially for ``micro-telluric" lines (shallow telluric absorption
lines with $<1$-3\% depths; \citealt{cunha2014}). As for spectral
region contaminated with deep telluric lines, typical precise RV
analysis usually gives

Previously, \cite{cunha2014} have characterized the effects of
micro-telluric contamination and proposed solution for the
ThAr-calibrated HARPS-S data.
